### 2022-09-01 sections/summary.tex
Update summary.tex

I am completing my DPhil (PhD) dissertation in the Department of Politics and International Relations and St Hilda’s College at the University of Oxford, United Kingdom. I am currently based in Oxford, working on my research. Furthermore, I am an Instructor Professor in the Management and Public Policies Department at the Faculty of Administration and Economics at the Universidad de Santiago de Chile (USACH).

Before starting the DPhil, in October 2019, I earned an MA (1st) in Political Science and a BA (2:1) in Government, both from the Universidad de Chile. Moreover, I served as a lecturer at the Universidad de Chile and a consultant for the United Nations Development Programme (UNDP).

>>>>

I am completing my DPhil (PhD) dissertation in the Department of Politics and International Relations and St Hilda’s College at the University of Oxford, United Kingdom. Before starting the DPhil, in October 2019, I earned an MA (1st) in Political Science and a BA (2:1) in Government, both from the Universidad de Chile. Moreover, I served as a lecturer at the Universidad de Santiago and Universidad de Chile and as a consultant for the United Nations Development Programme (UNDP).
